|

### 2019-12-15 article/letter.Rmd
changes in formatting, a few edits to text

---
title:
author:
date:
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

@@

We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer. Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns. We explain the precautions we have taken to ensure that the we correctly identify the effect of the TDP app on school outcomes. Second, we provide a thorough discussion of our additional data sources. More specifically, we show how the Brazilian Ministry of Education collects and publicises their data and indicate how our experiment uses that information to evaluate the robustness of our findings. We believe the new sections help give the results a clearer interpretation and strenghten our main arguments.

@@

Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.We believe our paper now reflects our results more accurately.

@@

>>>>

---
title:
author:
date:
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: no
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

@@

We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer. Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns. We explain the precautions we have taken to ensure that we correctly identify the effect of the TDP app on school outcomes. Second, we provide a thorough discussion of our additional data sources. More specifically, we show how the Brazilian Ministry of Education collects and publicises their data and indicate how our experiment uses that information to evaluate the robustness of our findings. We believe the new sections help give the results a clearer interpretation and strenghten our main arguments.

@@

Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses. We believe our paper now reflects our results more accurately.

@@

\newpage

# Editor Comments and Responses

**1)** The editor writes:

\noindent 
**Response:**

\begin{quotation}
Lorem ipsum.
\end{quotation}

\newpage

# Reviewer 1 Comments and Responses

**1)** Reviewer 1 writes:

\noindent
**Response:**
